---
title: "ICCS"
author: "Jenny"
date: "January, 2019"
output: 
  github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10)

library(tidyverse)
library(readr)
library(purrr)
library(writexl)
```


## Introduction

This file documents the data cleaning for the ICCS 1999-2009-2016 Citizenship Norms Project

Note that for citizenship norm recodes in all three survey waves, the norms are coded in the descending mean order of the 1999 data: obey,rights,local,work,envir,vote,history,respect,news,protest,discuss,party


## 1999 data loading and merging

1999 data: https://www.icpsr.umich.edu/icpsrweb/civicleads/studies/21661/datadocumentation  
Downloaded Jan 17, 2019

Load 1999 country files, in chronological order of file names. Bind all 1999 files. Note, total observations of resulting tbl1 (93,882) concur with xls documentation of expected total n


```{r}

# all files
files <- list.files("../data", full.names = TRUE)

# helper function to load files
load_files <- function(file) {
  e <- new.env()
  load(file, envir = e)
  
  stopifnot(length(e) == 1)  # safety first
  
  get(names(e)[1], envir = e)
}

tbl1 <- files %>%
  magrittr::extract(1:28) %>%      # filter to 1999 files only
  map(~ .x %>%
        load_files() %>%
        select(COUNTRY, IDCNTRY, IDSTUD, BS3B1, BS3B11, BS3B9, BS3B4, BS3B13,
               BS3B2, BS3B6, BS3B10, BS3B8, BS3B5, BS3B12, BS3B3, GENDER,BSGBOOK, EXPEDUC, BSGEDUM, BSGEDUF, TOTWGT)) %>% 
  reduce(rbind) %>% 
  as_tibble() %>% 
  mutate(`ICCS_year` = 1999) %>%     # add survey year variable
  select(`ICCS_year`, everything())
```


Cit norm, count all indicators to begin recode.

```{r}

original_vars <- tbl1 %>% 
  select(BS3B1, BS3B11, BS3B9, BS3B4, BS3B13, BS3B2, BS3B6, BS3B10, BS3B8, BS3B5, BS3B12, BS3B3) %>% 
  colnames() 

original_vars %>% 
  map(~ tbl1 %>% count(!!sym(.x)))
```


Cit norm, count and recode 1st indicator as example.

```{r}

# recode
tbl1 <- tbl1 %>% 
  mutate(BS3B1_binary = fct_collapse(BS3B1, 
  "not important" = c("(1) not important", "(2) somewhat unimportant"),
  "important"     = c("(3) somewhat important", "(4) very important")))

# confirm correct recode
tbl1 %>%
  count(BS3B1, BS3B1_binary) 
```


Repeat for all all cit norm indicators. NOTE: BS3B12 recoded separately below b/c of typo in string variable.
```{r}

tbl1 <-tbl1 %>% 
  mutate_at(vars(BS3B1, BS3B11, BS3B9, BS3B4, BS3B13, BS3B2, BS3B6, BS3B10, BS3B8, BS3B5, BS3B3),
            funs(bin = fct_collapse(.,
                                    "not important"= c("(1) not important", "(2) somewhat unimportant"),
                                    "important"    = c("(3) somewhat important", "(4) very important")))
  )
```

BS3B12 error troubleshoot when included in prior chunk. Count table command below yields console output showing that string text of 1st category "importnat"  spelled incorrectly, i.e. "a" and "n" transposed.  BS3B12 "mutate" command to correctly recode with this typo:

```{r}

# troubleshoot
tbl1 %>% count(BS3B12) 

# recode
tbl1 <- tbl1 %>% 
  mutate(BS3B12_bin = fct_collapse(BS3B12, 
                                   "not important" = c("(1) not importnat", "(2) somewhat unimportant"),
                                   "important"     = c("(3) somewhat important", "(4) very important"))
  )
```

Confirm successful mutates for all cit norms indicators.

```{r}

bin_vars <- original_vars %>% 
  paste0("_bin")

map2(original_vars, bin_vars, ~ tbl1 %>% count(!!sym(.x), !!sym(.y)))
```

Recode of individual-level control vars

```{r}

tbl1 <- tbl1 %>% 
  mutate(female = ifelse(GENDER == "(0) Male", 0, 1),    # gender
         books = case_when(                              # books in respondent's home
           BSGBOOK == "(1) None"          ~ 0,
           BSGBOOK == "(2) 1 - 10"        ~ 0,
           BSGBOOK == "(3) 11 - 50"       ~ 1,
           BSGBOOK == "(4) 51 - 100"      ~ 1,
           BSGBOOK == "(5) 101 - 200"     ~ 2,
           BSGBOOK == "(6) More than 200" ~ 3
         ),
         edexp = case_when(                              # expected number of additional educ years
           EXPEDUC == "(0) 0"    ~ 0,
           EXPEDUC == "(1) 1-2"  ~ 0,
           EXPEDUC == "(2) 3-4"  ~ 0,
           EXPEDUC == "(3) 5-6"  ~ 1,
           EXPEDUC == "(4) 7-8"  ~ 1,
           EXPEDUC == "(5) 9-10" ~ 2,
           EXPEDUC == "(6) 10+"  ~ 2
         ),
         ed_mom = case_when(                             # mother education
           BSGEDUM == "(1) no.elem.school"          ~ 0,
           BSGEDUM == "(2) Fin. elem. sch."         ~ 0,
           BSGEDUM == "(3) Fin.s.high sch."         ~ 0,
           BSGEDUM == "(4) Fin.high sch."           ~ 1,
           BSGEDUM == "(5) Sme technic.educ. after" ~ 2,
           BSGEDUM == "(6) sme college,univ."       ~ 2,
           BSGEDUM == "(7) bach. degree"            ~ 2
         ),
         ed_dad = case_when(                             # father education
           BSGEDUF == "(1) No.elem.school"     ~ 0,
           BSGEDUF == "(2) Fin. elem. sch."    ~ 0,
           BSGEDUF == "(3) Fin.s.high sch."    ~ 0,
           BSGEDUF == "(4) Fin.high sch."      ~ 1,
           BSGEDUF == "(5) Sme techn.educ."    ~ 2,
           BSGEDUF == "(6) Sme college, univ." ~ 2,
           BSGEDUF == "(7) Bach. degree"       ~ 2
         )) 

# check recodes
sociodem_vars <- c("GENDER", "BSGBOOK", "EXPEDUC", "BSGEDUM", "BSGEDUF")
recoded_vars  <- c("female", "books", "edexp", "ed_mom", "ed_dad")

map2(recoded_vars, sociodem_vars, ~ tbl1 %>% count(!!sym(.x), !!sym(.y)))
```

Select for LCA vars tibble, including rename all mutated variables and display first five lines of dataframe.

```{r}

tbl1 <- tbl1 %>%
  select(ICCS_year,
         COUNTRY,
         IDSTUD,
         TOTWGTS = TOTWGT,
         obey    = BS3B1_bin,
         rights  = BS3B11_bin,
         local   = BS3B9_bin,
         work    = BS3B4_bin,
         envir   = BS3B13_bin,
         vote    = BS3B2_bin,
         history = BS3B6_bin,
         respect = BS3B10_bin,
         news    = BS3B8_bin,
         protest = BS3B5_bin,
         discuss = BS3B12_bin,
         party   = BS3B3_bin,
         female,
         books,
         edexp,
         ed_mom,
         ed_dad)

tbl1 %>% head()
```


## 2009 dataloading and merging

2009 data: https://www.icpsr.umich.edu/icpsrweb/ICPSR/studies/36997 
Downloaded Jan 17, 2019

Load 2009 country files, in chronological order of file names. Bind all 2009 files; Note, total observations of resulting tbl2 (140,650) concur with xls documentation of expected total n.

```{r}

tbl2 <- files %>%
  magrittr::extract(29:66) %>%      # filter to 2009 files only
  map(~ .x %>%
        load_files() %>%
        select(COUNTRY, IDCNTRY, IDSTUD, IS2P21L, IS2P21I, IS2P21H, IS2P21K, IS2P21J, IS2P21A,
               IS2P21C, IS2P21E, IS2P21D, IS2P21G, IS2P21F, IS2P21B, SGENDER, IS2G11, IS2G03, IS2G07, IS2G09, TOTWGTS)) %>% 
  reduce(rbind) %>% 
  as_tibble() %>% 
  mutate(`ICCS_year` = 2009) %>%     # survey year variable creation
  select(`ICCS_year`, everything())
```

Cit norm, count all indicators to begin recode.

```{r}

original_vars <- tbl2 %>% 
  select(IS2P21L, IS2P21I, IS2P21H, IS2P21K, IS2P21J, IS2P21A, IS2P21C, IS2P21E, IS2P21D, IS2P21G, IS2P21F, IS2P21B) %>% 
  colnames() 

original_vars %>% 
  map(~ tbl2 %>% count(!!sym(.x)))
```

Recode all cit norm indicators. 

```{r}

tbl2 <- tbl2 %>% 
  mutate_at(vars(IS2P21L, IS2P21I, IS2P21H, IS2P21K, IS2P21J, IS2P21A, IS2P21C, IS2P21E, IS2P21D, IS2P21G, IS2P21F, IS2P21B),
            funs(bin = fct_collapse(.,
                                    "not important" = c("(3) NOT VERY IMPORTANT", "(4) NOT IMPORTANT AT ALL"),
                                    "important"     = c("(1) VERY IMPORTANT", "(2) QUITE IMPORTANT")))
  )
```

Confirm successful recodes.

```{r}

bin_vars <- original_vars %>% 
  paste0("_bin")

map2(original_vars, bin_vars, ~ tbl2 %>% count(!!sym(.x), !!sym(.y)))
```

Recode of individual-level control vars

```{r}

tbl2 <- tbl2 %>% 
  mutate(female = ifelse(SGENDER == "(0) BOY", 0, 1),    # gender
         books = case_when(                              # books in respondent's home
           IS2G11 == "(1) 0-10 BOOKS"          ~ 0,
           IS2G11 == "(2) 11-25 BOOKS"         ~ 1,
           IS2G11 == "(3) 26-100 BOOKS"        ~ 1,
           IS2G11 == "(4) 101-200 BOOKS"       ~ 2,
           IS2G11 == "(5) 201-500 BOOKS"       ~ 3,
           IS2G11 == "(6) MORE THAN 500 BOOKS" ~ 3
         ),
         edexp = case_when(                              # expected number of additional educ years
           IS2G03 == "(1) <ISCED 5A OR 6>"      ~ 2,
           IS2G03 == "(2) <ISCED 4 OR 5B>"      ~ 2,
           IS2G03 == "(3) <ISCED 3>"            ~ 1,
           IS2G03 == "(4) <ISCED 2>"            ~ 0,
           IS2G03 == "(5) NOT EXPECT <ISCED 2>" ~ 0
         ),
         ed_mom = case_when(                             # mother education
           IS2G07 == "(1) <ISCED 5A OR 6>"            ~ 2,
           IS2G07 == "(2) <ISCED 4 OR 5B>"            ~ 2,
           IS2G07 == "(3) <ISCED 3>"                  ~ 1,
           IS2G07 == "(4) <ISCED 2>"                  ~ 0,
           IS2G07 == "(5) <ISCED 1>"                  ~ 0,
           IS2G07 == "(6) DID NOT COMPLETE <ISCED 1>" ~ 0
         ),
         ed_dad = case_when(                             # father education
           IS2G09 == "(1) <ISCED 5A OR 6>"            ~ 2,
           IS2G09 == "(2) <ISCED 4 OR 5B>"            ~ 2,
           IS2G09 == "(3) <ISCED 3>"                  ~ 1,
           IS2G09 == "(4) <ISCED 2>"                  ~ 0,
           IS2G09 == "(5) <ISCED 1>"                  ~ 0,
           IS2G09 == "(6) DID NOT COMPLETE <ISCED 1>" ~ 0
         )) 

# check recodes
sociodem_vars <- c("SGENDER", "IS2G11", "IS2G03", "IS2G07", "IS2G09")
recoded_vars  <- c("female", "books", "edexp", "ed_mom", "ed_dad")

map2(recoded_vars, sociodem_vars, ~ tbl2 %>% count(!!sym(.x), !!sym(.y)))
```

Select for LCA vars tibble, including rename all mutated variables and display first five lines of dataframe.

```{r}

tbl2 <- tbl2 %>%
  select(ICCS_year,
         COUNTRY,
         IDSTUD,
         TOTWGTS,
         obey    = IS2P21L_bin,
         rights  = IS2P21I_bin,
         local   = IS2P21H_bin,
         work    = IS2P21K_bin,
         envir   = IS2P21J_bin,
         vote    = IS2P21A_bin,
         history = IS2P21C_bin,
         respect = IS2P21E_bin,
         news    = IS2P21D_bin,
         protest = IS2P21G_bin,
         discuss = IS2P21F_bin,
         party   = IS2P21B_bin,
         female,
         books,
         edexp,
         ed_mom,
         ed_dad) 

tbl2 %>% head()
```


## 2016 data loading and merging

2016 data: https://www.icpsr.umich.edu/icpsrweb/ICPSR/studies/37147 
Downloaded Jan 21, 2019

2016 country files, in chronological order of file names. Bind all 2016 country files. Note, total observations of resulting tbl (94,603) concur with xls documentation of expected total n.

```{r}

tbl3 <- files %>%
  magrittr::extract(67:90) %>%      # filter to 2016 files only
  map(~ .x %>%
        load_files() %>%
        select(COUNTRY, IDCNTRY, IDSTUD, IS3G23L, IS3G23I, IS3G23H, IS3G23K, IS3G23J,
               IS3G23A, IS3G23C, IS3G23E, IS3G23D, IS3G23G, IS3G23F, IS3G23B, S_GENDER, IS3G11, IS3G03, IS3G07, IS3G09, TOTWGTS)) %>% 
  reduce(rbind) %>% 
  as_tibble()%>% 
  mutate(`ICCS_year` = 2016) %>%    # create survey year variable
  select(`ICCS_year`, everything())
```

Cit norm, count all indicators to begin recode.

```{r}

original_vars <- tbl3 %>% 
  select(IS3G23L, IS3G23I, IS3G23H, IS3G23K, IS3G23J, IS3G23A, IS3G23C, IS3G23E, IS3G23D, IS3G23G, IS3G23F, IS3G23B) %>% 
  colnames() 

original_vars %>% 
  map(~ tbl3 %>% count(!!sym(.x)))
```


Recode all cit norm indicators. 

```{r}

tbl3 <- tbl3 %>% 
  mutate_at(vars(IS3G23L, IS3G23I, IS3G23H, IS3G23K, IS3G23J, IS3G23A, IS3G23C, IS3G23E, IS3G23D, IS3G23G, IS3G23F, IS3G23B),
            funs(bin = fct_collapse(.,
                                    "not important" = c("(3) Not very important", "(4) Not important at all"),
                                    "important"     = c("(1) Very important", "(2) Quite important")))
  )
```

Confirm successful mutates.

```{r}

bin_vars <- original_vars %>% 
  paste0("_bin")

map2(original_vars, bin_vars, ~ tbl3 %>% count(!!sym(.x), !!sym(.y)))
```

Recode of individual-level control vars

```{r}

tbl3 <- tbl3 %>% 
  mutate(female = ifelse(S_GENDER == "(0) BOY", 0, 1),   # gender
         books = case_when(                              # books in respondent's home
           IS3G11 == "(1) None or very few (0–10 books)"                                ~ 0,
           IS3G11 == "(2) Enough to fill one shelf (11–25 books)"                       ~ 1,
           IS3G11 == "(3) Enough to fill one bookcase (26–100 books)"                   ~ 1,
           IS3G11 == "(4) Enough to fill two bookcase (101–200 books)"                  ~ 2,
           IS3G11 == "(5) Enough to fill three or more bookcases (more than 200 books)" ~ 3
         ),
         edexp = case_when(                              # expected number of additional educ years
           IS3G03 == "(1) <ISCED level 6, 7 or 8>"   ~ 2,
           IS3G03 == "(2) <ISCED level 4 or 5>"      ~ 2,
           IS3G03 == "(3) <ISCED level 3>"           ~ 1,
           IS3G03 == "(4) <ISCED level 2> or below" ~ 0
         ),
         ed_mom = case_when(                             # mother education
           IS3G07 == "(1) <ISCED level 6, 7 or 8>"              ~ 2,
           IS3G07 == "(2) <ISCED level 4 or 5>"                 ~ 2,
           IS3G07 == "(3) <ISCED level 3>"                      ~ 1,
           IS3G07 == "(4) <ISCED level 2>"                      ~ 0,
           IS3G07 == "(5) She did not complete <ISCED level 2>" ~ 0
         ),
         ed_dad = case_when(                             # father education
           IS3G09 == "(1) <ISCED level 6, 7 or 8>"             ~ 2,
           IS3G09 == "(2) <ISCED level 4 or 5>"                ~ 2,
           IS3G09 == "(3) <ISCED level 3>"                     ~ 1,
           IS3G09 == "(4) <ISCED level 2>"                     ~ 0,
           IS3G09 == "(5) He did not complete <ISCED level 2>" ~ 0
         )) 

# check recodes
sociodem_vars <- c("S_GENDER", "IS3G11", "IS3G03", "IS3G07", "IS3G09")
recoded_vars  <- c("female", "books", "edexp", "ed_mom", "ed_dad")

map2(recoded_vars, sociodem_vars, ~ tbl3 %>% count(!!sym(.x), !!sym(.y)))
```

Select for LCA vars tibble, including rename all mutated variables and display first five lines of dataframe.

```{r}

tbl3 <- tbl3 %>% 
  select(ICCS_year,
         COUNTRY,
         IDSTUD,
         TOTWGTS,
         obey    = IS3G23L_bin,
         rights  = IS3G23I_bin,
         local   = IS3G23H_bin,
         work    = IS3G23K_bin,
         envir   = IS3G23J_bin,
         vote    = IS3G23A_bin,
         history = IS3G23C_bin,
         respect = IS3G23E_bin,
         news    = IS3G23D_bin,
         protest = IS3G23G_bin,
         discuss = IS3G23F_bin,
         party   = IS3G23B_bin,
         female,
         books,
         edexp,
         ed_mom,
         ed_dad)

tbl3 %>% head()
```


## Combining recoded 1999, 2009 and 2016 data frames 

Combine the three data frames and create unique id per observation across binded country files to be able to import Latent Gold class assignment for each unique observation.

```{r}

tbl <- rbind(tbl1, tbl2, tbl3) %>% 
  mutate(id  = row_number(),
         id2 = paste0(COUNTRY, IDSTUD))
```

Check number of observations by survey year of the combined data frame.
```{r}

# number of observations by survey year
tbl %>% 
  count(ICCS_year) %>% 
  knitr::kable()
```

Separate into different country-year `.dat` files for separate LG analysis.  There are 90 different country-year combinations.  We will save these files in `/output/country-year/`.

```{r}
tbl %>% 
  mutate(country_year = paste0(COUNTRY, "-", ICCS_year)) %>% 
  group_by(country_year) %>% 
  group_walk(~ write_delim(.x, paste0("output/country-year/", .y$country_year, ".dat"), delim = ","))
```

Quick check files contain what we expect.

```{r}
all.equal(tbl %>% filter(COUNTRY == "AUS", ICCS_year == 1999) %>% mutate_if(is.integer, as.numeric) %>% mutate_if(is.factor, as.character),
          read_delim("output/country-year/AUS-1999.dat", delim = ",") %>% mutate_if(is.integer, as.numeric) %>% mutate_if(is.factor, as.character))
```


## Exporting final combined datafile

Before exporting, convert citizenship norm indicators to integer (0 = "not important", 1 = "important").

```{r}

cit_norm_indicators <- vars(obey, rights, local, work, envir, vote, history, respect, news, protest, discuss, party)

tbl <- tbl %>% 
  mutate_at(cit_norm_indicators,
            funs(as.integer(case_when(
              . == "not important" ~ 0,
              . == "important"     ~ 1
            )))
  ) %>% 
  mutate_at(vars(ICCS_year, IDSTUD), as.integer) %>% 
  mutate(COUNTRY = as.character(COUNTRY))

tbl %>% head()
```

We can also attach factor labels to the citizenship norm indicators for internal use in R, but won't export the factor labels to the output text file (we'd have to save as an R object .e.g `.rds`).  An example of how we can do this:

```{r}

example <- tbl %>% 
  mutate_at(cit_norm_indicators,
            funs(haven::labelled(., labels = c("not important" = 0, "important" = 1))))

# cit norm indicator vars are now int+lbl type
example %>% 
  glimpse()

# access labels by converting those vars to factors
example %>% 
  mutate_at(cit_norm_indicators, funs(as_factor(.)))
```


Adding country-level (level-2) variables for multi-level regression. For 1999 and 2009, includes all 21 countries from IJCS paper

GDP 1998: gdp_imf98

```{r}
tbl <- tbl %>% 
  mutate(gdp_imf98=case_when(
	COUNTRY ==	"BGR"	&  ICCS_year == 1 ~	1622.98,
	COUNTRY ==	"CHE"	&  ICCS_year == 1 ~	39304.07,
	COUNTRY ==	"CHL"	&  ICCS_year == 1 ~	5437.33,
	COUNTRY ==	"COL"	&  ICCS_year == 1 ~	2770.85,
	COUNTRY ==	"CYP"	&  ICCS_year == 1 ~	13829.8,
	COUNTRY ==	"CZE"	&  ICCS_year == 1 ~	6200.85,
	COUNTRY ==	"DNK"	&  ICCS_year == 1 ~	32796.45,
	COUNTRY ==	"ENG"	&  ICCS_year == 1 ~	25275.21,
	COUNTRY ==	"EST"	&  ICCS_year == 1 ~	4021.33,
	COUNTRY ==	"FIN"	&  ICCS_year == 1 ~	25184.63,
	COUNTRY ==	"GRC"	&  ICCS_year == 1 ~	12654.18,
	COUNTRY ==	"HKG"	&  ICCS_year == 1 ~	25734.93,
	COUNTRY ==	"ITA"	&  ICCS_year == 1 ~	21547.92,
	COUNTRY ==	"LTU"	&  ICCS_year == 1 ~	3170.75,
	COUNTRY ==	"LVA"	&  ICCS_year == 1 ~	2858.356,
	COUNTRY ==	"NOR"	&  ICCS_year == 1 ~	34036.022,
	COUNTRY ==	"POL"	&  ICCS_year == 1 ~	4448.938,
	COUNTRY ==	"RUS"	&  ICCS_year == 1 ~	1837.544,
	COUNTRY ==	"SVK"	&  ICCS_year == 1 ~	4177.291,
	COUNTRY ==	"SVN"	&  ICCS_year == 1 ~	11004.326,
	COUNTRY ==	"SWE"	&  ICCS_year == 1 ~	28768.349
))

tbl %>% 
 count(gdp_imf98)
```



GDP 2008: gdp_imf08 

```{r}
tbl <- tbl %>% 
  mutate(gdp_imf08=case_when(
  COUNTRY	==	"BGR"	&  ICCS_year == 2 ~ 6849.48,
  COUNTRY ==	"CHE"	&  ICCS_year == 2 ~	67378.87,
  COUNTRY ==	"CHL"	&  ICCS_year == 2 ~	10813.74,
  COUNTRY ==	"COL"	&  ICCS_year == 2 ~	5174.09,
  COUNTRY ==	"CYP"	&  ICCS_year == 2 ~	32194.93,
  COUNTRY ==	"CZE"	&  ICCS_year == 2 ~	21040.64,
  COUNTRY ==	"DNK"	&  ICCS_year == 2 ~	67386.89,
  COUNTRY ==	"ENG"	&  ICCS_year == 2 ~	45681,
  COUNTRY ==	"EST"	&  ICCS_year == 2 ~	18809.06,
  COUNTRY ==	"FIN"	&  ICCS_year == 2 ~	54577.85,
  COUNTRY ==	"GRC"	&  ICCS_year == 2 ~	33433.84,
  COUNTRY ==	"HKG"	&  ICCS_year == 2 ~	31849.05,
  COUNTRY ==	"ITA"	&  ICCS_year == 2 ~	40449.6,
  COUNTRY ==	"LTU"	&  ICCS_year == 2 ~	14456.17,
  COUNTRY ==	"LVA"	&  ICCS_year == 2 ~	14930.12,
  COUNTRY ==	"NOR"	&  ICCS_year == 2 ~	102524.55,
  COUNTRY ==	"POL"	&  ICCS_year == 2 ~	14892.8,
  COUNTRY ==	"RUS"	&  ICCS_year == 2 ~	12578.52,
  COUNTRY ==	"SVK"	&  ICCS_year == 2 ~	18584.56,
  COUNTRY ==	"SVN"	&  ICCS_year == 2 ~	28328.22,
  COUNTRY ==	"SWE"	&  ICCS_year == 2 ~	55623.77
  ))

tbl %>% 
 count(gdp_imf08)
  
```

**JO noting additional stata code on this var:
gen GDP08 = GDP_IMF08/100 // divided by 100							
egen GDP_m08 = mean(GDP08)							
gen GDP_c08 = GDP08 - GDP_m08							




Democracy 1998: demo_98
Notes from stata do-file: Years of democracy based on POLITY IV dataset (2011)

```{r}

tbl <- tbl %>% 
  mutate(demo_98=case_when(
	COUNTRY ==	"BGR"	&  ICCS_year == 1999 ~	10,
	COUNTRY ==	"CHE"	&  ICCS_year == 1999 ~	82,
	COUNTRY ==	"CHL"	&  ICCS_year == 1999 ~	11,
	COUNTRY ==	"COL"	&  ICCS_year == 1999 ~	21,
	COUNTRY ==	"CYP"	&  ICCS_year == 1999 ~	29,
	COUNTRY ==	"CZE"	&  ICCS_year == 1999 ~	7,
	COUNTRY ==	"DNK"	&  ICCS_year == 1999 ~	77,
	COUNTRY ==	"ENG"	&  ICCS_year == 1999 ~	82,
	COUNTRY ==	"EST"	&  ICCS_year == 1999 ~	15,
	COUNTRY ==	"FIN"	&  ICCS_year == 1999 ~	68,
	COUNTRY ==	"GRC"	&  ICCS_year == 1999 ~	40,
	COUNTRY ==	"ITA"	&  ICCS_year == 1999 ~	52,
	COUNTRY ==	"LTU"	&  ICCS_year == 1999 ~	9,
	COUNTRY ==	"LVA"	&  ICCS_year == 1999 ~	14,
	COUNTRY ==	"NOR"	&  ICCS_year == 1999 ~	77,
	COUNTRY ==	"POL"	&  ICCS_year == 1999 ~	17,
	COUNTRY ==	"RUS"	&  ICCS_year == 1999 ~	0,
	COUNTRY ==	"SVK"	&  ICCS_year == 1999 ~	2,
	COUNTRY ==	"SVN"	&  ICCS_year == 1999 ~	9,
	COUNTRY ==	"SWE"	&  ICCS_year == 1999 ~	82,
	TRUE ~ NA_real_     #-------- Everything else will be missing
  ))

tbl %>% 
 count(demo_98)

```

Additional stata code for var used in ML reg:
egen D_m98 = mean(DEMO_98) // center
gen D_c98 = DEMO_98 - D_m98 // center

```{r}

#--------- We don't need the intermediat variable D_m98, do centering in one step

tbl <- tbl %>%
  mutate(D_c98 = scale(demo_98, scale = F))  #------- If scale = T, new variable will have variance = 1

```

Democracy 2008: demo_08
Notes from stata do-file: Years of democracy based on POLITY IV dataset (2011)
```{r}

tbl <- tbl %>% 
  mutate(demo_08=case_when(
	COUNTRY ==	"BGR"	&  ICCS_year == 2009 ~	19,
	COUNTRY ==	"CHE"	&  ICCS_year == 2009 ~	90,
	COUNTRY ==	"CHL"	&  ICCS_year == 2009 ~	20,
	COUNTRY ==	"COL"	&  ICCS_year == 2009 ~	21,
	COUNTRY ==	"CYP"	&  ICCS_year == 2009 ~	38,
	COUNTRY ==	"CZE"	&  ICCS_year == 2009 ~	16,
	COUNTRY ==	"DNK"	&  ICCS_year == 2009 ~	85,
	COUNTRY ==	"ENG"	&  ICCS_year == 2009 ~	90,
	COUNTRY ==	"EST"	&  ICCS_year == 2009 ~	24,
	COUNTRY ==	"FIN"	&  ICCS_year == 2009 ~	76,
	COUNTRY ==	"GRC"	&  ICCS_year == 2009 ~	49,
	COUNTRY ==	"ITA"	&  ICCS_year == 2009 ~	61,
	COUNTRY ==	"LTU"	&  ICCS_year == 2009 ~	18,
	COUNTRY ==	"LVA"	&  ICCS_year == 2009 ~	23,
	COUNTRY ==	"NOR"	&  ICCS_year == 2009 ~	85,
	COUNTRY ==	"POL"	&  ICCS_year == 2009 ~	26,
	COUNTRY ==	"RUS"	&  ICCS_year == 2009 ~	0,
	COUNTRY ==	"SVK"	&  ICCS_year == 2009 ~	11,
	COUNTRY ==	"SVN"	&  ICCS_year == 2009 ~	18,
	COUNTRY ==	"SWE"	&  ICCS_year == 2009 ~	90,
	TRUE ~ NA_real_
  ))

tbl %>% 
 count(demo_08)

```

Create centered version.

```{r}

tbl <- tbl %>%
  mutate(D_c08 = scale(demo_98, scale = F))

```

Additional stata code for var used in ML reg:
egen D_m08 = mean(DEMO_08) // center
gen D_c08 = DEMO_08 - D_m08 // center

**JO Next step coding task, create variables for 2015 for "gdp_imf15" and 
"demo_15"
Identify data on IMF site, and document in xls for all countries in the 2016 wave



Export recoded data for LCA - RdM to current `ICCS-2019/clean-data` directory.

```{r}

write_delim(tbl, "output/clean_tbl.dat", delim = ",")

```

At this point, LCA was performed in LatentGold.  The results were saved, now join them back into the original data.  Data were created on a European computer, so decimals points are commas, which everybody knows is as wrong as saying the second floor is the first floor, but Europeans are just that way.  In addition, the output uses "." to denote missing.  To keep it simple, only save the cluster variables.

```{r}

lca_tbl <- read_tsv("../lcadata/tbl_14_wclass.dat", locale = locale(decimal_mark = ","), na = ".") %>%
  dplyr::select(ICCS_year, COUNTRY, id, id2, `Cluster#1`:`Cluster#`)



tbl <- tbl %>%
  left_join(lca_tbl)


```



## Tables:

Means of citizenship norm indicators by country and year.

```{r}

# count and percent of responses to "obey" grouped by year
means <- tbl %>%
  group_by(COUNTRY, ICCS_year) %>% 
  summarize_at(cit_norm_indicators, funs(round(mean(., na.rm = TRUE), 3)))

means %>% 
  knitr::kable()
```

Count and percentage of missing values for each indicator by country and year.

```{r}

missing <- tbl %>% 
  group_by(COUNTRY, ICCS_year) %>% 
  summarize_at(cit_norm_indicators,
               funs(paste0(sum(is.na(.)), " (", (round(sum(is.na(.)) / length(.) * 100, 2)), "%)")))

missing %>% 
  knitr::kable()
```

Write tables to excel.

```{r}

write_xlsx(list(means = means, missing = missing), "output/citizenship-norm-indicator-tables.xlsx")
```


## Figures:

#### Means for twelve citizenship norm indicators for only the 14 countries that are included in all three waves of the survey.

First, create the table to be used for plotting.

```{r, warning = FALSE}
all_wave_countries <- tbl %>%
  count(COUNTRY, ICCS_year) %>% 
  count(COUNTRY) %>%
  filter(n == 3) %>% 
  pull(COUNTRY)

# table with lower and upper limits for error bars
plot_tbl <- tbl %>% 
  filter(COUNTRY %in% all_wave_countries) %>% 
  group_by(ICCS_year) %>% 
  summarize_at(cit_norm_indicators, funs(t.test(.) %>%
                                           broom::tidy() %>%
                                           mutate(mean_ci = paste(estimate, conf.low, conf.high)) %>%
                                           pull(mean_ci))) %>% 
  gather(Indicator, value, -ICCS_year) %>% 
  mutate(value = str_split(value, " "),
         cols = map(value, ~ data.frame(t(.)))) %>% 
  unnest(cols) %>% 
  select(-value) %>% 
  mutate(mean  = as.numeric(X1),
         lower = as.numeric(X2),
         upper = as.numeric(X3)) %>% 
  select(-c(X1, X2, X3))

plot_tbl %>% 
  mutate_if(is.numeric, round, 3) %>% 
  knitr::kable()

```

Line plots:

```{r line-plots-all}

# line plot with year on x-axis, lines colored by indicator type
plot_tbl %>% 
  ggplot(aes(x = ICCS_year, y = mean, group = Indicator, colour = Indicator)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .3) +
  geom_line() +
  geom_point() +
  lims(y = c(0, 1)) +
  labs(x = "Year", y = "Mean", title = "Mean Citizenship Norm Indicators By Survey Year") 

ggsave("output/mean-citizenship-norm-line-plot-by-year.png")
```

If we want to do this in black and white, we can just add the `theme_bw()` option at the end.  In addition, we'll need to change the "color" aesthetic to something else.  Switching it to `lty` gives a different line type for each `Indicator`.

```{r}

plot_tbl %>% 
  ggplot(aes(x = ICCS_year, y = mean, lty = Indicator)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .3) +
  geom_line() +
  geom_point() +
  lims(y = c(0, 1)) +
  labs(x = "Year", y = "Mean", title = "Mean Citizenship Norm Indicators By Survey Year") +
  theme_bw()

```

The above plot includes all indicators on one plot, but the confidence intervals are so narrow they are hard to see for each individual indicator.  An alternative way to present the same data is to plot them separately and `facet_wrap()` the plots so they are all in one image.

```{r line-plots-facet-1}
# line plot with year on x-axis, lines colored by indicator type
plot_tbl %>% 
  ggplot(aes(x = ICCS_year, y = mean, group = Indicator, colour = Indicator)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  geom_line() +
  geom_point() +
  facet_wrap(~Indicator, scales = "free") +
  labs(x = "Year", y = "Mean", title = "Mean Citizenship Norm Indicators By Survey Year") +
  theme(legend.position = "none")

ggsave("output/mean-citizenship-norm-line-plot-by-year-facet.png")
```



Adapting y-axis to consistent

```{r line-plots-facet-2}
# line plot with year on x-axis, lines colored by indicator type
plot_tbl %>% 
  ggplot(aes(x = ICCS_year, y = mean, group = Indicator, colour = Indicator)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  geom_line() +
  geom_point() +
  facet_wrap(~Indicator, scales = "fixed") +
  labs(x = "Year", y = "Mean", title = "Mean Citizenship Norm Indicators By Survey Year") +
  theme(legend.position = "none")

ggsave("output/mean-citizenship-norm-line-plot-by-year-facet.png")
```



Re-ordering to highest mean top left

```{r line-plots-facet-3}
# line plot with year on x-axis, lines colored by indicator type
plot_tbl %>% 
  mutate(Indicator=fct_relevel(Indicator,c("obey", "rights", "local", "work", "envir", "vote", "history", "respect", "news", "protest", "discuss", "party"))) %>% 
  ggplot(aes(x = ICCS_year, y = mean, group = Indicator, colour = Indicator)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  geom_line() +
  geom_point() +
  facet_wrap(~Indicator, scales = "fixed") +
  labs(x = "Year", y = "Mean", title = "Mean Citizenship Norm Indicators By Survey Year") +
  theme(legend.position = "none")

ggsave("output/mean-citizenship-norm-line-plot-by-year-facet.png")
```


Adding specific years on x-axis

```{r line-plots-facet-4}
# line plot with year on x-axis, lines colored by indicator type
plot_tbl %>% 
  mutate(Indicator=fct_relevel(Indicator,c("obey", "rights", "local", "work", "envir", "vote", "history", "respect", "news", "protest", "discuss", "party"))) %>% 
  ggplot(aes(x = ICCS_year, y = mean, group = Indicator, colour = Indicator)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  geom_line() +
  geom_point() +
  facet_wrap(~Indicator, scales = "fixed") +
  labs(x = "Year", y = "Mean", title = "Mean Citizenship Norm Indicators By Survey Year") +
  theme(legend.position = "none", axis.text.x = element_text(size=7)) +
  scale_x_continuous(breaks=c(1999, 2009, 2016))

ggsave("output/mean-citizenship-norm-line-plot-by-year-facet.png")
```

Bar plots:

```{r}

# bar plot with indicators on x-axis, lines colored by year
plot_tbl %>% 
  mutate(Year      = as.factor(ICCS_year),
         Indicator = factor(Indicator, ordered = TRUE, levels = c("obey", "rights", "local", "work", "envir", "vote", "history",
                                                                  "respect", "news", "protest", "discuss", "party"))) %>% 
  ggplot(aes(x = Indicator, y = mean, fill = Year)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5, position = position_dodge(.9)) +
  labs(x = "Indicator", y = "Mean", title = "Mean Citizenship Norm Indicators By Survey Year")

ggsave("output/mean-citizenship-norm-bar-plot-by-indicator.png")
```


#### Means for twelve citizenship norm indicators in 2016 by country

Looking at 2016 data only, plot means for all cit norm indicators by country.

```{r, warning = FALSE}

country_plot_tbl <- tbl %>% 
  filter(ICCS_year == 2016) %>% 
  group_by(COUNTRY) %>% 
  summarize_at(cit_norm_indicators, funs(t.test(.) %>%
                                           broom::tidy() %>%
                                           mutate(mean_ci = paste(estimate, conf.low, conf.high)) %>%
                                           pull(mean_ci))) %>% 
  gather(Indicator, value, -COUNTRY) %>% 
  mutate(value = str_split(value, " "),
         cols = map(value, ~ data.frame(t(.)))) %>% 
  unnest(cols) %>% 
  select(-value) %>% 
  mutate(mean  = as.numeric(X1),
         lower = as.numeric(X2),
         upper = as.numeric(X3),
         Indicator = factor(Indicator, ordered = TRUE, levels = c("obey", "rights", "local", "work", "envir", "vote", "history",
                                                                  "respect", "news", "protest", "discuss", "party"))) %>% 
  select(-c(X1, X2, X3))

country_plot_tbl %>% 
  head()
```

Plot with countries on x-axis, `facet_wrap` by indicator.

```{r, fig.height = 35}
country_plot_tbl %>% 
  ggplot(aes(x = COUNTRY, y = mean, fill = COUNTRY)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5, position = position_dodge(.9)) +
  facet_wrap(~Indicator, scales = "free", ncol = 1) +
  labs(x = "Indicator", y = "Mean", title = "Mean Citizenship Norm Indicators in 2016 By Country") +
  theme(legend.position = "none")

ggsave("output/mean-citizenship-norm-bar-plot-by-country-by-indicator-2016-only.png")
```


March 6, 2019: JO noting next steps for analysis now that LCA results are complete.



## Mixed Models

Sample code for linear mixed model:

```{r, eval = F}

library(lme4)

lin_mixed <- lmer(dv ~ iv1 + iv2 + (1 | COUNTRY), data = tbl)
summary(lin_mixed)

```

Mixed effects logit:

```{r, eval = F}

lin_mixed <- glmer(dv ~ iv1 + iv2 + (1 | COUNTRY), data = tbl, family = binomial(link = "logit"))
summary(lin_mixed)

```